The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2020-03-31 razzo-abstract.tex
Abstract

% Two or three sentences explaining what
% the main result reveals in direct
% comparison to what was thought to be the case
% previously, or how the main result adds to
% previous knowledge.
We show that the extent of the inference error increases with the number of multiple birth events, as expected.
\rampal{We need a bit more reults here}

% One or two sentences to put the results into a
% more general context.
These results allow phylogeneticists to judge under which circumstances the standard tree priors can be safely used, and under what circumstances phylogenetic inferences are unreliable. \giovanni{Not entirely sure if this is the best sentence to put here.}
\rampal{Would be nice if we gave some guidelines here}

>>>>

% Two or three sentences explaining what
% the main result reveals in direct
% comparison to what was thought to be the case
% previously, or how the main result adds to
% previous knowledge.
We show that the extent of the inference error 
does not notably increase with the number of multiple birth events.
Instead, the phylogenetic inference fails to converge more
often under these settings.
This reduced convergence is profound and easily detectable,
yet its cause is unknown.

% One or two sentences to put the results into a
% more general context.
These results show that using standard tree priors for biological systems
following a species pump model is warranted, as long as convergence can 
be attained. For settings that do not converge, the addition of 
a new species tree prior to the current phylogenetic software may resolve this.
